### 2017-05-18 sheets/basis-3/sheet-basis-3.tex
minor stylistic changes to sheet 3.
Remove exercise 5 and add a new exercise about category equivialences to the top

@@

\begin{exercise}

  \begin{definition}{Canonical according to Leinster}
     "Canonical is an informal word, meaning something like 'God-given' or
    'defined without making arbitrary choices'.  For example, for any two sets
    $A$ and $B$, there is a canonical bijection $A \times B \to B \times A$
    defined by $(a, b) \mapsto (b, a)$, and there is a canonical function $A
    \times B \to A$ defined by $(a, b) \mapsto a$.  But the function $B \to A$
    defined by 'choose an element $a_0 \in A$ and send everything to $a_0$' is
    not canonical, because the choice of $a_0$ is arbitrary."
  \end{definition}
	Let $A$ and $B$ be sets, and denote by $B^A$ the set of functions from $A$
	to $B$.  Write down:
	\begin{itemize}
		\item[(a)] a canonical function $A \to B^{(B^A)}$,
		\item[(b)] a canonical function $A \times B^{A} \to B$.
	\end{itemize}
\end{exercise}

@@

\begin{exercise}
	Let the following natural transformations be given:
	\[
\xymatrix{
\cat{A}
\ruppertwocell<8>^F{\alpha}
\ar[r]|G
\rlowertwocell<-8>_H{\beta} &
\cat{A}'
\ruppertwocell<8>^{F'}{\hspace{.2em}\alpha'}
\ar[r]|{G'}
\rlowertwocell<-8>_{H'}{\hspace{.2em}\beta'} &
\cat{A}''
}
\]
Now prove that the interchange law holds, that is
\[
(\beta' \of \alpha') * (\beta \of \alpha)
=
(\beta' * \beta) \of (\alpha' * \alpha)
\]
\end{exercise}

>>>>

\begin{exercise}
  Define categories $\cat{A}$ and $\cat{B}$ such that either $\cat{A} \iso \cat{B}$ in $\CAT$ or $\cat{A} \eqv \cat{B}$, but not both.
  Do not use the example given during the lecture.
\end{exercise}

@@

\begin{definition}{Canonical according to Leinster}
  "Canonical is an informal word, meaning something like 'God-given' or
  'defined without making arbitrary choices'.  For example, for any two sets
  $A$ and $B$, there is a canonical bijection $A \times B \to B \times A$
  defined by $(a, b) \mapsto (b, a)$, and there is a canonical function $A
  \times B \to A$ defined by $(a, b) \mapsto a$.  But the function $B \to A$
  defined by 'choose an element $a_0 \in A$ and send everything to $a_0$' is
  not canonical, because the choice of $a_0$ is arbitrary."
\end{definition}

\begin{exercise}
  Let $A$ and $B$ be sets, and denote by $B^A$ the set of functions from $A$
  to $B$.  Write down:
  \begin{itemize}
  \item[(a)] a canonical function $A \to B^{(B^A)}$,
  \item[(b)] a canonical function $A \times B^{A} \to B$.
  \end{itemize}
\end{exercise}

@@
